Realistically Interesting Domains for Probabilistic Planners

### 2014-04-09 FinalPaper/paper.tex
Consistent use of separation lines
Less use of IPPC in the domains

%--------------------------------------------------------------------

@@

%---------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------------------------------------

@@

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC and compare that with the UAV domain. Since
Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
of domains, domains of the IPPC competition have shifted to those
probabilistically interesting domains, which are difficult for replanners.
Often domains that don't pass this test are deemed to be classical planners in
disguise, favoring the use of replanners.

\subsection{IPPC Domains}

\subsubsection{Blocksworld}

A simple domain used in the competition of 2004 is the well known blocksworld
domain. The uncertainty lies in that the gripper, used to move blocks, has a
probability that it drops the blocks to the table. Another difference is that
the blocks are colored, and the goal is to build a tower of certain colored
blocks, rather than a tower with specific blocks. If for example there are
four blue blocks, and the goal is a tower of three blue blocks, it does not
matter which blue blocks are used.

\subsubsection{Navigation}

The navigation domain represents a grid in which a robot must reach a goal.
Every cell offers the robot a different chance of disappearing. The robot needs
to choose a path which gets it to the goal most reliably within the finite
horizon time \cite{sanner2011navigation}.

\subsubsection{Traffic}

This domain represents a simple binary version of the cell transition model
(CTM) for modelling traffic based on the original CTM Tech Report
\cite{sanner2011traffic}. Because of the binary variables and no intermediate
variable restrictions, this model is simplified and ignores traffic aspects
such as turns and turn probabilities. This model also uses concurrent actions
and the total actions has an upper bound of $2^{\#~of~intersections}$.

\subsubsection{Elevators}

The IPPC-06 has an elevators domain, however we describe the latest IPPC-11
elevators domain. In this domain there are a number of elevators delivering
passengers to either the top or bottom floor. Potential passengers arrive at
any floor at a certain rate (depending on which floor). The elevators can only
move in the direction it is indicating, so passengers know whether to board or
not. The goal of the elevators is to transport as many as possible passengers
to their destinations.

\subsubsection{SysAdmin}

The SysAdmin domain describes a network of connected servers. Each server has
a probability that it shuts down, and if is not running, it has a probability
to reboot. The probability that a server shuts down depends on the number of
running connected servers.

@@

The IPPC-11 domains, Navigation, Traffic, Elevators and SysAdmin are finite-
horizon domains. Navigation, however, is actually a goal oriented domain, if
the goal is reached in the horizon. The method how this is implemented is that
the goal state is defined as an absorbing state, and there is no reward or cost
associated to staying in the goal state, until the horizon is reached.

\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track
winner PROST by far on goal-oriented domains Navigation and Crossing Traffic
\cite{kolobov2012gourmand}. PROST however mildly outperforms \textsc{Gourmand}
on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to
perform expensive Bellman Backups on these domains that include large branching
factors.

The reason \textsc{Gourmand} performs quite well on the navigation domain is
because it uses a dynamic lookahead.

@@

\subsection{\textsc{Glutton}}
The \textsc{Glutton} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques. It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$. It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$. It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both. It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
Since \textsc{Glutton} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling. To compensate for these states, \textsc{Glutton} has to resort to a \emph{default policy}. \todo{Wel of niet de default policy uitleggen}.
%---------------------------------------------------------------------

>>>>

%------------------------------------------------------------------------------

@@

%------------------------------------------------------------------------------

@@

%------------------------------------------------------------------------------

@@

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC and compare that with the UAV domain. Since
Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
of domains, domains have shifted to those probabilistically interesting
domains, which are difficult for replanners. Often domains that don't pass
this test are deemed to be classical planners in disguise, favoring the use of
replanners.

\paragraph{Blocksworld:}
A simple domain used in the competition of 2004 is the well known blocksworld
domain. The uncertainty lies in that the gripper, used to move blocks, has a
probability that it drops the blocks to the table. Another difference is that
the blocks are colored, and the goal is to build a tower of certain colored
blocks, rather than a tower with specific blocks. If for example there are
four blue blocks, and the goal is a tower of three blue blocks, it does not
matter which blue blocks are used.

\paragraph{Navigation:}
The navigation domain represents a grid in which a robot must reach a goal.
Every cell offers the robot a different chance of disappearing. The robot needs
to choose a path which gets it to the goal most reliably within the finite
horizon time \cite{sanner2011navigation}.

\paragraph{Traffic:}
This domain represents a simple binary version of the cell transition model
(CTM) for modelling traffic based on the original CTM Tech Report
\cite{sanner2011traffic}. Because of the binary variables and no intermediate
variable restrictions, this model is simplified and ignores traffic aspects
such as turns and turn probabilities. This model also uses concurrent actions
and the total actions has an upper bound of $2^{\#~of~intersections}$.

\paragraph{Elevators:}
The elevators domain has evaluated between the competitions of 2006 and
2011, we describe the latest version. In this domain there are a number of
elevators delivering passengers to either the top or bottom floor. Potential
passengers arrive at any floor at a certain rate (depending on which floor).
The elevators can only move in the direction it is indicating, so passengers
know whether to board or not. The goal of the elevators is to transport as many
as possible passengers to their destinations.

\paragraph{SysAdmin:}
The SysAdmin domain describes a network of connected servers. Each server has
a probability that it shuts down, and if is not running, it has a probability
to reboot. The probability that a server shuts down depends on the number of
running connected servers.

@@

The newer  domains, Navigation, Traffic, Elevators and SysAdmin are finite-
horizon domains. Navigation, however, is actually a goal oriented domain, if
the goal is reached in the horizon. The method how this is implemented is that
the goal state is defined as an absorbing state, and there is no reward or cost
associated to staying in the goal state, until the horizon is reached.

\textsc{Gourmand} vastly outperformed the UCT-based PROST, the IPPC-11
probabilistic track winner, by far on goal-oriented domains Navigation and
Crossing Traffic \cite{kolobov2012gourmand}. This is because of the dynamic
lookahead feature of \textsc{Gourmand}. PROST however mildly outperforms
\textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT
does not need to perform expensive Bellman Backups on these domains that
include large branching factors.

@@

\subsection{\textsc{Glutton}}
The \textsc{Glutton} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques. It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$. It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$. It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both. It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
Since \textsc{Glutton} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling. To compensate for these states, \textsc{Glutton} has to resort to a \emph{default policy}. \todo{Wel of niet de default policy uitleggen}.

%------------------------------------------------------------------------------
